{{ cookiecutter.paper_title}}

### 2018-08-26 {{ cookiecutter.repo_name }}/Paper/paper.tex
Fixed typos

%% Program-specific configuration
% PDF settings
\hypersetup{
    pdfauthor={{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name}},
    pdftitle={{ cookiecutter.paper_title}},
    pdfkeywords={cosmology: observations --- cosmology: large-scale structure 
            of Universe --- galaxies: groups --- galaxies:clusters
            --- methods: statistical, machine learning},
    colorlinks=true,
    citecolor=blue,
    linkcolor=magenta,
    urlcolor=cyan
}

@@

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \href{mailto:{{ cookiecutter.author_email }}}{ {{ cookiecutter.author_email.replace('_', '\_' ) }} } }\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}

>>>>

%% Program-specific configuration
% PDF settings
\hypersetup{
    pdfauthor={{ cookiecutter.author_name }},
    pdftitle={{ cookiecutter.paper_title}},
    pdfkeywords={cosmology: observations --- cosmology: large-scale structure 
            of Universe --- galaxies: groups --- galaxies:clusters
            --- methods: statistical, machine learning},
    colorlinks=true,
    citecolor=blue,
    linkcolor=magenta,
    urlcolor=cyan
}

@@

%% Author
\author[{{ cookiecutter.author_last_name + ' et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \href{mailto:{{ cookiecutter.author_email }}}{ {{ cookiecutter.author_email.replace('_', '\_' ) }} } }\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}
